Individual Variation in Animal Movement and Effects on Seed Dispersal Distance

### 2021-01-15 paper/paper.Rmd
Section on weibull distribution for the methods

>>>>

Seed dispersal kernels are functions used to describe the probability of a seed being dispersed or deposited at a specific distance away from its parent plant [@nathan_spatial_2000]. The resulting data from our three simulation models provided a dispersal distance for each simulated seed, and thus we used this information to describe the seed dispersal kernels for each model (null, individual, and family). Dispersal kernels in nature tend to be leptokurtic, with a peak near the origin and long tails, therefore kernel shape can be summarized by its kurtosis [@morales_effects_2006]. We quantified the dispersal kernels produced in our models by the sample statistics of mean and kurtosis to describe the overall shape and tail of distribution of seed dispersal distances. In addition to this, we also fit a Weibull distribution via maximum likelihood to obtain estimates of the shape and scale parameters in this distribution. This probability distribution is commonly used in dispersal ecology and has been shown to be flexible enough to accommodate variability in the tails and provide informative parameters associated to the mean dispersal distance and fatness of the tail [@morales_effects_2006]. We fit the data associated to seed dispersal distances produced by each of the three models via Maximum Likelihood using the Weibull density function associated with the package 'fitdistrplus'[@fitdistrplus]:
$$W(x) = \left(\frac{a}{b}\right) \left(\frac{x}{b}\right)^{a-1} exp[-(x/{b})^{a}]$$

Where the shape parameter $a$ determines the tail of the distribution, and $b$ is the scale parameter. It is worth mentioning that the standard parameterization of the Weibull in 'R' is different from the parameterization used in Morales and Carlo [-@Morales_effects_2006], where the shape parameter $a = \nu$ remains the same, but the scale parameter is defined as $\kappa = b^{-\nu}$, giving a density distribution function of $W(r)= \kappa\nu r^{\nu-1} exp[-{\kappa r}^\nu]$. Here, we report the scale parameter following the alternative parameterization, but the original values returned after fitting the Weibull distribution using R can be found in the Supplementary Table 1. Since the shape parameter remains the same, we can note that for $a=\nu=1$ the distribution shows a tail with exponential decay, with values of $\nu <1$ the tail shows fast-decay, and when $\nu>1$ we can see a fat-tailed distribution (Fig 2.) We visually assessed the fit of the distributions via qqplots and used the Kolmogorov-Smirnov statistic to assess goodness of fit (Supplementary information).

Fig 2. Capation: Variation in Weibull distributions determined by the value of the shape parameter. The scale parameter is defined as $b=1$, and the shape parameters are defined as follows: solid line $a=\nu=1$ shows an exponential decay tail, dashed line $a=\nu=0.2$ shows a thin tail, and $a=\nu=2$ describes a fat tail with the dotted line.

```{r}
library(ggplot2)

# shape
exptail <- 1
thintail <- 0.2
fattail <- 2

#scale
b <- 1
kappaexp <- b^-exptail
kappathin <- b^-thintail
kappafat <- b^-fattail

ggplot(data = data.frame(x = c(0.1, 4)), aes(x)) +
  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = thintail),
                color = "black", linetype = "dashed", size = 1.2) +
  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = exptail), 
                color = "black", linetype = "dotted", size = 1.2) +
  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = fattail),
                color = "black", linetype = "solid", size = 1.2) +
  ylab("") +
  theme_bw()
